Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-05-18 ms.tex
put in results of the first amplifier flip test. I am surprised that it didn't help more because the 4 channels look highly correlated.

\subsubsection{Other Reference Channel Subtraction}
We note that the 4 channels have very similar 1/f correlation behavior, as shown in Figure \ref{fig:darkPixelTimeSeries}.
Another option to remove 1/f noise is to subtract the illuminated amplifier with a target in it by unilluminated channels.

\begin{figure*}[!hbtp]
\centering
\includegraphics[width=.4\columnwidth]{pixeltime_series.pdf}
\caption{The time series for all 4 amplifiers is very similar due to shared 1/f noise behavior.
This is visible in a short segment of the time series of all pixels for an example group up the ramp (53) in a dark ramp where the bias has already been subtracted.}\label{fig:darkPixelTimeSeries}
\end{figure*}

>>>>

\subsubsection{Other Reference Channel Subtraction}
We note that the 4 channels have very similar 1/f correlation behavior, as shown in Figure \ref{fig:darkPixelTimeSeries}.
Another option to remove 1/f noise is to subtract the illuminated amplifier with a target in it by unilluminated channels.
We attempt to subtract an amplifier 0's time series from all amplifiers.
Of course, this means that this amplifier is perfectly subtracted and no noise or signal remains in this 1/4 of the image.
The subtraction step should increase the read noise on an individual pixel by $\sim \sqrt{2}$ because the errors from the subtracted pixel should add in quadrature to the original pixels.
However, this increase in read noise on a per-pixel level might be acceptable if it decreases the correlated errors along the rows.

This method increases the noise over a row-by-row median subraction.
The standard deviations in the time series range from 8,500 DN to 10,800 DN for this reference amplifier method as opposed to the 5,500 DN to 6,600 DN for a row-by-row median.
This means the the correlations within an amplifier are not efficiently subracted (\textbf{\textcolor{red}{or there was an error in the code. I'm surprised that it didn't make a bigger difference.}}).
\begin{figure*}[!hbtp]
\centering
\includegraphics[width=.4\columnwidth]{pixeltime_series.pdf}
\caption{The time series for all 4 amplifiers is very similar due to shared 1/f noise behavior.
This is visible in a short segment of the time series of all pixels for an example group up the ramp (53) in a dark ramp where the bias has already been subtracted.}\label{fig:darkPixelTimeSeries}
\end{figure*}
